\bf Estimating the number of clusters using cross-validation

### 2019-01-11 JCGS-R2/cvclust.tex
caption scree plot

\begin{figure}
\centering
\begin{minipage}{\linewidth}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\linewidth]{main_code/demo/elbow/correct-data.pdf}
  \end{minipage}
  \hspace{0.05in}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\linewidth]{main_code/demo/elbow/correct-withinss.pdf}
  \end{minipage}
\end{minipage}
\begin{minipage}{\linewidth}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\linewidth]{main_code/demo/elbow/incorrect-data.pdf}
  \end{minipage}
  \hspace{0.05in}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\linewidth]{main_code/demo/elbow/incorrect-withinss.pdf}
  \end{minipage}
\end{minipage}
\caption{Left panels show the $(X,Y)$ data points; right panels
  show the corresponding values of the within-cluster sum of squares $W_k$
plotted against the number of clusters, $k$.}
\label{fig:elbow}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{minipage}{\linewidth}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\linewidth]{main_code/demo/elbow/correct-data.pdf}
  \end{minipage}
  \hspace{0.05in}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\linewidth]{main_code/demo/elbow/correct-withinss.pdf}
  \end{minipage}
\end{minipage}
\begin{minipage}{\linewidth}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\linewidth]{main_code/demo/elbow/incorrect-data.pdf}
  \end{minipage}
  \hspace{0.05in}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\linewidth]{main_code/demo/elbow/incorrect-withinss.pdf}
  \end{minipage}
\end{minipage}
\caption{Scree plots for two data sets. Left panels show the sets of
    two-dimensional data points, generated from four clusters, with plotting
    symbol indicating the generated cluster. Right panels show the
    corresponding values of the within-cluster sum of squares $W_k$
    plotted against the number of clusters, $k$. The scree plot identifies
    the correct number of clusters in the top row, but fails in the bottom
    row.}
\label{fig:elbow}
\end{figure}
